Tugas Pak Farit

### 2024-05-05 Project/Tugas-Pak-Farit.Rmd
Update

norm_samples <- lapply(sample_size, function(n) rnorm(n, mean=60, sd=4))

@@

unif_samples <- lapply(sample_size, function(n) runif(n, min=0, max=1))

@@

exp_samples <- lapply(sample_size, function(n) rexp(n, rate=1))

>>>>

norm_samples <- lapply(sample_n, function(n) rnorm(n, mean=60, sd=4))

@@

unif_samples <- lapply(sample_n, function(n) runif(n, min=0, max=1))

@@

exp_samples <- lapply(sample_n, function(n) rexp(n, rate=1))
